Serious Titles are Boring: predicting the future of dark matter halos is fun.

### 2019-01-18 PaperText.tex
Mostly text edits

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{textgreek}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Abbie=Smart Person]{The Crystal Ball of Halo Mergers (Not serious title don't worry)}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[K. T. Smith et al.]{
Genius 1,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
Genius 2,$^{2}$
and Genius 3$^{2,3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

% Abstract of the paper
\begin{abstract}
Using machine learning, we predict the survival, mass loss, final position, and merging time of subhalos within a dark matter only simulation. Given many recent works questioning the accuracy of individual subhalo fates due to numerical disruption in simulations and differences in halo finder or merger tree code, we use the ability of these models to accurately make predictions as a proxy for the stochasticity of the underlying evolution within N-body simulations. Survival is well predicted, with 96.5\% accuracy given only 3 parameters from the initial interaction. Mass loss is more stochastic, with 90\% of subhalos being predicted accurately, given the definition of accuracy allows a \textpm 20\% error in mass. For final position, 90\% of subhalos can be predicted accurately given the definition of accuracy allows a \textpm 20\% error in final location. For merge time, 90\% of subhalos can be predicted accurately given an error of \textpm 1.5 dynamical times. We conclude that the evolution of individual subhalos within N-body simulations is quite stochastic. \textit{Probably should have more than just that one conclusion. Something like "But, it's encouraging that...."}
\end{abstract}

@@

According to the standard \LambdaCDM model of cosmology, dark matter structures in the universe form hierarchically through series of mergers, with larger halos continuously growing through the accretion of smaller subhalos. Once independent halos themselves, these subhalos sink to the center of their "host" halos, losing mass along their orbits due to tidal effects and dynamical friction. However, as has been shown by modern cosmological N-body simulations (CITE, CITE, CITE), a significant number of such subhalos retain some of their mass, remaining as substructures within their hosts today. The study of these substructures has been fundamental to our understanding of many areas of astrophysics, including the formation and evolution of galaxies (CITE, CITE), which relies on both accurate populations of subhalos for applications such as abundance matching (CITE, CITE), and accurate subhalo evolution for applications such as semi-analytic modeling (CITE, CITE).

Although the evolution and statistics of dark matter structures is most often studied from high-resolution cosmological N-body simulations, much speculation remains as to the accuracy of these simulations, particularly on these small scales (Van den Bosch 2018, VDB 2016, everything VDB's done pretty much). Although several studies have suggested that simulation resolution only effects subhalos with fewer than 50-100 particles (CITE, CITE, CITE), \citet{VDB2018} found that typical state-of-the-art cosmological simulations cannot resolve subhalos well enough to follow their mass loss until complete disruption. In the Bolshoi simulation, \citet{VDB2016} found that only around 20\% of subhalo disruption was truly physical, with instantaneous masses of the subhalos along their orbits being highly erratic. Similarly, \citet{VDB2017} found that most subhalo disruption in modern simulations is artificial or numerical in nature.

A number of other works have also called into question the reliability of the halo catalogs and merger trees that are generated from these simulations. Comparison projects have found differing results for the fates of subhalos using different halo finders (\citet{Knebe2011}, \citet{Avila2013}) and merger tree codes (\citet{Srisawat2013}, CITE). Because these codes fundamentally define subhalos in different ways and trace their properties between snapshots using different methods, these comparison projects found that, when applied to the same simulation, resulting halo catalogs and merger trees could differ quite significantly. \textit{A few more specific examples, in each case. Need more citations/projects.}

Although subhalo mass functions seem to be consistent amongst different simulations and with the use of these different codes, down to small subhalo masses (CITE, CITE), the evolution and fate of an individual subhalo remains much harder to predict. Nonetheless, semi-analytic models, attempt to describe the evolution of subhalos, tuning their analytic equations to the results of N-body simulations (CITE, CITE, CITE). These semi-analytic models often perform quite well, reproducing the ... \textit{Also need to look up more SAM citations for this section. Talk about producing populations vs individual subs. Challenges of getting a specific subs evolution correct.}

Although semi-analytic models face challenges in predicting the individual fates of subhalos, much work has been done to pinpoint the parameters necessary to model subhalo evolution and the physical processes that cause such evolution. \textit{Cover each topic? Works on merge time. Works on survival. Works on mass loss. Works on final position. As inidivudal paragraphs? A sentence?}

In this work, we use a merger tree generated from the dark matter only simulation VISHNU (CITE?), and the subhaloes within it, in order to determine the fate (i.e Survival, Mass Loss, Merging Time, Final Position) of a subhalo from its initial conditions at the time of entering its host. Using physically-motivated parameters from the time of the subhalos entry, we use machine learning to predict these final quantities of the subhalo, in the hopes of investigating to what degree subhalo fate is motivated by these parameters and to what degree the interaction is stochastic and cannot be predicted. Assuming a generalized analytic model to predict the fate of a subhalo exists, a machine learning algorithm should be able to approximate this functional form and map the subhalo fate to its initial conditions. Otherwise, given stochasticity in individual subhalo fate resulting from numerical disruption and halo identification problems, many of the subhalos will not be able to be predicted accurately. \textit{This feels very weirdly worded and/or not really concise. Need to revisit.}

\textit{I don't know if parts of this paragraph really needs to be here or if it just goes without saying that machine learning is a cool tool.} Recently in astrophysics, the use of machine learning has become increasingly popular for such applications (CITE, CITE, CITE). The ability of machine learning models to approximate any function, given a complete set of parameters, means it is an incredibly useful tool when a direct analytic function cannot be found. Notably, \citet{Nadler2017} recently used machine learning to predict the survival or disruption of subhalos in a hydrodynamic simulation, using the initial conditions of their counterparts in a dark matter only simulation. They were quite successful, accurately predicting the results of 85\% of their subhalo population. Works like this are encouraging that machine learning can be used to fit these complicated interactions. However, in this work, although we only use a dark matter only simulation, we also hope to take our predictions a step further by also predicting the mass loss, final spatial position, and merging time of these subhalos.

@@

\section{Simulation/Description Of Data}
\label{sec:simulation}
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{Figures/explanatory_figures}
    \caption{An example of a surviving (top) and merging (bottom) interaction between a subhalo and host halo. The orbit of these two subhalos are shown within the virial radius of their respective host halos. Size of points along the orbit correspond to the mass of the subhalo. In order to see the orbits and the size of the points more clearly, we have plotted only every eighth timestep of the subhalo's orbit. Quantities that we try to predict in this work are labeled and numbered in the order they will be presented throughout the paper.}
    \label{fig:explanatory_figures}
\end{figure}

	Our analysis makes use of VISHNU, a cosmological N-body simulation with 1000 snapshots. VISHNU contains 1680\textsuperscript{3} particles in a volume of 130h\textsuperscript{-1} cMpc and uses WMAP-1 cosmology (\citet{Spergel2013}; $\Omega$\textsubscript{m} = 0.25, $\Omega$\textsubscript{$\Lambda$} = 0.75, $\Omega$\textsubscript{b} = 0.04, $\sigma$\textsubscript{8} = 0.8, \textit{n\textsubscript{s}} = 1.0, \textit{h} = 0.7). Each dark matter particle has mass \textit{m\textsubscript{p}} = 3.215 $\times$ 10\textsuperscript{7}h\textsuperscript{-1} M\textsubscript{\(\odot\)}, and subhalos can contain as few as 2 particles. The ROCKSTAR halo finder was used to identify halos and subhalos, and merger trees were constructed with Consistent-Trees (\citet{Behroozi2013b}).

@@

    From the merger trees, we select subhalos of the most massive progenitors of host halos at \textit{z}=0. These subhalos are allowed to have further substructure inside of them but cannot, at any point during their infall, become sub-substructure themselves. To help mitigate resolution uncertainties, we select only subhalos which consist of 1000 particles (total mass 3.215 $\times$ 10\textsuperscript{10}h\textsuperscript{-1} M\textsubscript{\(\odot\)}) or more at their time of accretion. We define the accretion point of a subhalo as the last timestep before a subhalo enters its host. As such, at the initial time of accretion, the will-be subhalos are still host halos themselves. Once the subhalo has entered its host, however, it cannot leave again (so, a flyby interaction would not be considered on its first pass but will be considered on a later pass if it falls back into and remains inside the host). Once it has been accreted, the subhalo must have one of two fates: merge with the host, or remain a bound, identified subhalo within that host until today. Following uncertainties in subhalo mass loss shown by \citet{VDB2018}, once a subhalo has lost more than 90\% of its mass, it is considered to be merged.

@@

    In addition to making cuts for resolution, some merging interactions were removed due to their unphysical behavior, likely as a result of errors in the merger trees. \textbf{INSERT NUMBER} Subhalos were removed that gained more than 10 times their mass (\textit{or some threshold.. I don't know yet what's best yet}) during infall. These subhalos likely had their identifications changed as they moved close to the center of the host. \textbf{INSERT NUMBER} subhalos were removed because their initial mass was larger than that of its supposed host. \textbf{INSERT NUMBER} subhalos were removed because their positions were outside of their host's virial radius after periodic boundary conditions were corrected for. \textbf{INSERT NUMBER} subhalos were removed because their time of merging was earlier than their time of entry?? \textit{Show a few cases of these strange orbits/mass loss histories??}

@@

	Although we have attempted to correct for these errors, there remains the possibility that erroneous cases still exist within our sample. We have made a hard cut to remove halos that gain mass, but there may be still be cases where an identification of a halo was changed within our sample. Possible other cases we found: Weird looking orbits that weren't in initial filtering. Some discussion of the cases that could possibly still exist in the data due to difficulty in being able to filter them out/ find a general way to search for them? \textit{Something that gives some estimation of how many cases might be like this? To ensure that it's not some large part of the sample and the reason we can't predict things. Mention that we removed about 2\% of the total number so even if you assume the same portion is wrong it shouldn't be the source of the stochasticity?}

@@

    Our resulting sample includes a total of \textbf{INSERT NUMBER} subhalo-halo interactions. Distributions of this sample with respect to host masses, mass ratios, and the scale factor of the time of entry are shown in Fig.~\ref{fig:combined_distributions_logBin}. The most common interactions in our sample are mergers of lower mass ratio that occurred more recently. However, our sample also spans the space of more equal mass and higher redshift mergers, with hundreds of interactions shown in many of the bins in Fig.~\ref{fig:combined_distributions_logBin}. \textit{Some reference to how many of these are expected? Indication that this is a representative sample of what we expect to see slash agreement with other simulations?}

@@

    For both the host halo and subhalo at the timestep of infall, and at either the timestep right before merging or at z=0, we take several physically-motivated parameters to describe the interaction between the halos. Table 1 lists these parameters and includes a brief description of each. \textit{Include ALL parameters that we took and then somehow mark the ones that we kept or only mention the ones that we kept. I don't want a table of a billion things but also don't want any question that we didn't cover everything}. From the parameters taken from the merger trees, we calculated some additional parameters. These include the eccentricity, mass ratio (M\textsubscript{ratio}=M\textsubscript{sub}/M\textsubscript{host}), relative distances and relative velocities? \textit{How much to go over these, or do we even need to mention calculating stuff like relative distance because it's so obvious.} Initial parameters, which were used as input parameters to the machine learning models to make predictions, include:

    \begin{itemize}
        \item \textbf{a}: the scale factor of the universe at the time of the subhalo's entry.
        \item \textbf{M\textsubscript{sub,i}}: the virial mass of the subhalo at the time of its entry.
        \item \textbf{M\textsubscript{host,i}}: the virial mass of the host halo at the time of the subhalo's entry.
        \item \textbf{M\textsubscript{sub,i}/M\textsubscript{host,i}}: the ratio of subhalo to host halo masses at the time of the subhalo's entry.
        \item \textbf{R\textsubscript{vir,sub,i}}: the virial radius of the subhalo
        \item \textbf{R\textsubscript{vir,host,i}}: the virial radius of the host halo
        \item \textbf{c\textsubscript{sub}}: the concentration of the subhalo
        \item \textbf{c\textsubscript{host}}: the concentration of the host halo
        \item \textbf{\textlambda\textsubscript{sub}}: Bullock spin parameter of the subhalo
        \item \textbf{\textlambda\textsubscript{host}}: Bullock spin parameter of the host halo
        \item \textbf{v\textsubscript{rel}}: relative total velocity between subhalo and host halo, calculated in the reference frame of the sub.
        \item \textbf{d\textsubscript{rel,i}}: relative absolute total distance between subhalo and host halo centers
        \item \textbf{\textepsilon}: eccentricity of subhalos initial orbit
        \item \textbf{max(M\textsubscript{subs,sub})}: the virial mass of the most massive sub-subhalo within the subhalo at the time of the subhalo's entry. 0 if subhalo has no sub-substrucutre.
        \item \textbf{max(M\textsubscript{subs,host})}: the virial mass of the most massive subhalo already within the host halo at the time of the selected subhalo's entry. Does not include the selected subhalo.
        \item \textbf{N\textsubscript{subs,sub}}: the total number of sub-subhalos within the subhalo at the time of entry.
        \item \textbf{N\textsubscript{subs,host}}:  the total number of subhalos within the host halo at the time of entry. Does not include the selected subhalo.
        \item \textbf{T\textsubscript{sub}}: the triaxiality parameter of the subhalo at the time of entry.
        \item \textbf{T\textsubscript{host}}:  the triaxiality parameter of the host halo at the time of entry.
    \end{itemize}

    Parameters that are taken at the end of the interaction, either at the time of merging or at z=0, are used to define the quantities that the machine learning models will predict. These parameters include:

\renewcommand{\theenumi}{\arabic{enumi}}
    \begin{enumerate}
        \item \textbf{survival}: a 0 or 1, depending on if the subhalo exists above the required mass threshold at z=0 (survives, 1) or if the subhalo has merged with its host at some time before (merges, 0)
        \item \textbf{M\textsubscript{sub,f}}: the virial mass of the subhalo at the end of the interaction.
        \item \textbf{d\textsubscript{rel,f}}: relative absolute total distance between subhalo and host halo centers at the end of the interaction, normalized by the virial radius of the host halo.
        \item \textbf{t\textsubscript{merge}}: the elapsed time between entry of a subhalo into the host virial radius and the time of merging with the host.
    \end{enumerate}
\par
    As preparation for using machine learning, we split the data into train and test sets, with 80\% of the data to be used for training and 20\% to be used for testing. These subsamples are selected randomly from the total sample. \textit{Counts and some simple statistics of these sets are shown in Table 2. Averages and standard deviations of these samples are similar, showing that the test set is representative of the training set.} The data was also scaled and normalized to have a mean of zero and unit variance. For training the machine learning models, the training set was further divided into training and validation sets, also using an 80/20 split. From the original dataset, this means the data was split as 64\% training, 16\% validation, and 20\% testing.

\begin{figure*}[h]
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\textwidth]{Figures/combined_distributions_logbin}
    \caption{Distributions of the merging interactions within our sample, in two different two-dimensional spaces. The left panel shows the distribution of mergers in the space of the host mass (x-axis) and the mass ratio (y-axis) of the interaction. The right panel shows the distribution of mergers in the space of the scale of initial entry of the subhalo (x-axis) and again, the mass ratio of the interaction on the y-axis. Within each hexagonal bin, the counts of interactions are shown, on a logarithm scale, by the colorbar. Histograms show the one-dimensional distribution of host masses (above the left panel), scale of entry (above the right panel) and mass ratios to the right of the right panel). Most interactions occur at lower mass ratios and for smaller host halos, but the spaces are still well-spanned over a range of interactions in both panels. }
    \label{fig:combined_distributions_logBin}
\end{figure*}

\section{Machine Learning Methods}
\label{sec:ML Methods}
The machine learning algorithms used in this work come from the \texttt{scikit-learn} package for python. For the classification problem of subhalo survivial, we use the random forest algorithm. For the regression problems of predicting mass loss, final position, and merging time, we use the gradient boosting regressor algorithm. Although the reader is referred to the \texttt{scikit-learn} documentation for a full description of these algorithms, a brief description of these methods is included in this section.

>>>>

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{color}
\newcommand\khb[1]{{\color{blue}#1}}
\newcommand\edits[1]{{\color{red}#1}}
\newcommand\aab[1]{{\color{green}#1}}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{textgreek}
\usepackage{enumitem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Abbie=Smart Person]{Serious Titles are Boring: predicting the future of dark matter halos is fun.}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Very Smart]{
Genius 1,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
Genius 2,$^{2}$
and Genius 3$^{2,3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

% Abstract of the paper
\begin{abstract}
\khb{The evolution of a dark matter halo in a dark matter only simulation is governed purely by Newtonian gravity, making a clean testbed to determine what halo properties drive its fate. Using machine learning, we predict the survival, mass loss, final position, and merging time of subhalos within a cosmological N-body simulation,
focusing on what instantaneous features of the halo, interaction, and environment matter most.}

%using the ability of these models to accurately make predictions as a proxy for the stochasticity of the underlying subhalo evolution.

Survival is well predicted, with 96.5\% accuracy, given only 3 parameters from the initial interaction. However, the mass loss, final location, and merging times are much more stochastic processes, requiring the definition of accuracy to allow for larger errors in prediction to reach similar accuracy percentages \khb{huh? rephrase after the comma} The scale factor, orbital eccentricity, relative velocity, and the masses of the host and subhalo are the only relevant parameters for determining subhalo evolution. In general, subhalos that enter their hosts at a mid-range of initial scale factor (typically a = .6-.8) are most challenging to make predictions for, across all of our final outcomes. More circular subhalo orbits are also easier to predict, except for in the case of predicting disruption, where the opposite appears to be true. We conclude that the detailed evolution of individual subhalos within N-body simulations is quite stochastic, with implications... \khb{I'd prefer redshift to scale factor, because I think more people use z than a}
\end{abstract}

@@

\khb{looking at the Annual Reviews of Astronomy and Astrophysics can help here -- adding a few to get you started!, but this is definitely not complete}

According to the standard \LambdaCDM model of cosmology, dark matter structures in the universe form hierarchically through series of mergers, with larger halos continuously growing through the accretion of smaller subhalos. Once independent halos themselves, these subhalos sink to the center of their "host" halos, losing mass along their orbits due to tidal effects and dynamical friction. However, as has been shown by modern cosmological N-body simulations (CITE, CITE, CITE), a significant number of such subhalos retain some of their mass, remaining as substructures within their hosts today. The study of these substructures has been fundamental to our understanding of many areas of astrophysics, from large-scale structure (CITE, CITE) to the formation and evolution of galaxies (CITE, CITE), 
\khb{https://www.annualreviews.org/doi/abs/10.1146/annurev-astro-081817-051756, https://www.annualreviews.org/doi/abs/10.1146/annurev-astro-081913-040019}
which relies on both accurate subhalo populations and evolution within these cosmological simulations (CITE, CITE).

\khb{https://www.annualreviews.org/doi/abs/10.1146/annurev-astro-091916-055313?intcmp=trendmd}

\khb{looking at the Annual Reviews of Astronomy and Astrophysics can help here -- adding a few to get you started}

Galaxy formation and evolution is commonly studied through modeling the evolution of the subhalos that these galaxies inhabit, with tools such as semi-analytic models (CITE, CITE). 
\khb{https://www.annualreviews.org/doi/abs/10.1146/annurev-astro-082812-140951?intcmp=trendmd}
These techniques typically rely on merger trees constructed from N-body simulations, along with analytic treatments of the physical processes that cause their evolution (CITE, CITE, CITE). These semi-analytic models often perform quite well, reproducing the statistical properties of subhalo populations (CITE, CITE, CITE). Other works have focused on reproducing specific properties of subhalos, such as disruption rates (CITE, CITE, CITE), mass loss histories (CITE, CITE, CITE), spatial distributions within host halos (CITE, CITE, CITE), and merging timescales (CITE, CITE, CITE).

Although much work has been done to better model these processes and create prescriptions for subhalo evolution, the validity (\textit{doesn't seem like the right word}) of tuning models to the evolution within N-body simulations has remained relatively unexplored. N-body simulations produce consistent subhalo mass functions that have been shown to be converged down to small masses (CITE, CITE, CITE). However, it has not been explored in detail whether the evolution of an individual subhalo within these simulations is a truly deterministic process. These analytic models for subhalo evolution often rely on some set of parameters about the subhalo and host halo at the beginning of an interaction (CITE, CITE, CITE, CITE) to predict the final evolution of such subhalo. However, it may be that subhalo evolution within N-body simulations is a stochastic process, and interactions with similar properties do not necessarily behave in similar ways.

In this work, we use a merger tree generated from the dark matter only simulation VISHNU (CITE?) in order to determine the evolution and fate of subhalos, quantified by the aforementioned final quantities (i.e survival/disruption, mass loss, final location within host halo, merging timescale) using machine learning. We model these final conditions from initial conditions at the time of a subhalo entering its host. Using physically-motivated parameters from the time of the subhalos entry, we use machine learning to predict these final quantities of the subhalo, in the hopes of investigating to what degree subhalo fate is motivated by these parameters and to what degree the interaction is stochastic and cannot be predicted. If the mass loss from a subhalo is deterministic, a machine learning algorithm should be able to map subhalo fate to initial conditions. On the other hand, if there is a level of stochasticity in subhalo fate, whether from physics or from the simulation, there will remain large prediction errors, even when using a complete set of parameters. \textit{This feels very weirdly worded and/or not really concise. Need to revisit.}

Machine learning has emerged as a powerful tool in astrophysics in a variety of fields, such as gravitational wave data analysis, exoplanet detection, galaxy morphological classification, one more. (CITE, CITE, CITE). The ability of machine learning models to approximate any function using a large set of parameters provides a useful means of revealing complicated correlations when a direct analytic function cannot be found. Notably, \citet{Nadler2017} recently used machine learning to predict the survival or disruption of subhalos in a hydrodynamic simulation, using the initial conditions of their counterparts in a dark matter only simulation. They were quite successful, accurately predicting the results of 85\% of their subhalo population. Works like this are encouraging that machine learning can be used to fit these complicated interactions. \edits{However, in this work, although we only use a dark matter only simulation, we also hope to take our predictions a step further by also predicting the mass loss, final spatial position, and merging time of these subhalos.}

\texit{Not positive about this being here or in the section where I talk about the parameters we have? And how much to go through individual papers or just list off like: these are the most common ones for merge time: list, list, list, list (CITE, CITE, CITE, CITE) type deal. So for now, this is just an unfinished paragraph.}
As mentioned above, many works have already attempted to analytically model these subhalo evolution processes with much success. As such, we have selected similar or the same initial parameters that have been found to be important for subhalo evolution to use in our model. For subhalo survival, ....

@@

\section{Description of the Data}
\label{sec:simulation}
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{Figures/explanatory_figures}
	\vspace{-15pt}
    \caption{An example of a surviving (top) and merging (bottom) interaction between a subhalo and host halo. The orbit of these two subhalos are shown within the radius of their respective host halos, shown by the larger, unfilled circles. Point size corresponds to subhalo mass along the orbit, plotted at each eighth timestep. The green point and circle show initial quantities, at the timestep right before the subhalo enters its host. The purple point and circle show final quantities, at either the timestep right before the subhalo dissolves in the merging case, or at the final timestep in the simulation in the surviving case. Predicted quantities (light blue) are labeled and numbered in the order they will be presented throughout the paper.}
    \label{fig:explanatory_figures}
\end{figure}

	Our analysis makes use of VISHNU, a cosmological N-body simulation with 1000 snapshots for exquisite time resolution; no snapshot is separated by more than X years. VISHNU contains 1680\textsuperscript{3} particles in a volume of 130h\textsuperscript{-1} cMpc and uses WMAP-1 cosmology (\citet{Spergel2003}; $\Omega$\textsubscript{m} = 0.25, $\Omega$\textsubscript{$\Lambda$} = 0.75, $\Omega$\textsubscript{b} = 0.04, $\sigma$\textsubscript{8} = 0.8, \textit{n\textsubscript{s}} = 1.0, \textit{h} = 0.7). Each dark matter particle has mass \textit{m\textsubscript{p}} = 3.215 $\times$ 10\textsuperscript{7}h\textsuperscript{-1} M\textsubscript{\(\odot\)}, and the force resolution is X parsecs. The ROCKSTAR halo finder was used to identify halos and subhalos, and merger trees were constructed with Consistent-Trees (\citet{Behroozi2013}).

@@

    Starting with halos at \textit{z}=0, we use the merger trees to identify the most massive progenitors of all host halos within the simulation, and track the subhalos within. These subhalos are allowed to have further substructure inside of them but cannot, at any point during their infall, become sub-substructure themselves. To help mitigate resolution uncertainties, we select only subhalos with a minimum of 1000 particles (total mass 3.215 $\times$ 10\textsuperscript{10}h\textsuperscript{-1} M\textsubscript{\(\odot\)}) at their time of accretion. We define the accretion time as the last timestep before a subhalo enters its host. 
    %As such, at the initial time of accretion, the will-be subhalos are still host halos themselves. Once the subhalo has entered its host, however, it cannot leave again (so, a flyby interaction would not be considered on its first pass but will be considered on a later pass if it falls back into and remains inside the host). 
    Once it has been accreted, the subhalo must have one of two fates: merge with the host, or remain a bound, identified subhalo within that host until today. We define the point of merging as the point right before dissolution of the subhalo, the last timestep in the simulation where it is identified as its own entity. Following uncertainties in subhalo mass loss shown by \citep{VandenBosch2018}, once a subhalo has lost more than 90\% of its mass, we also consider it to be merged. This cut changes the fates of only a small number of our subhalos, \edits{around 5\%}, but ensures a more consistent definition of merging that is less sensitive to resolution errors. \edits{Counts before/after 1000 particle cut, and before/after this 90\% loss cut is made}.

@@

    Figure \ref{fig:explanatory_figures} shows examples of the orbits of the two types of interactions that we consider. In the top panel, we show an example of a surviving interaction, where the subhalo orbits for some time, losing mass but not dissolving before z=0. In the bottom panel, we show an example of a merging interaction, where the subhalo orbits and loses mass until reaching the center of the host and dissolving at some time before z=0. The four quantities that we will predict are shown in blue and numbered by the order that they will be presented in Section \ref{sec:Results}. We predict the survival of both the surviving and merging populations as one complete sample. When we predict the mass loss and final position quantities, we do so for only our surviving population. When we predict the merging time quantity, we do so for only the merging population. 

@@

    In addition to making cuts for resolution, some interactions were removed due to their unphysical behavior, likely as a result of errors in the merger tree generation or halo finding. \textbf{INSERT NUMBER} Subhalos were removed that gained more than 10 times their mass during infall. These subhalos were likely misidentified as they moved close to the center of the host, instead being assigned the mass of another subhalo or the host itself. \textbf{INSERT NUMBER} subhalos were removed because their initial mass was larger than that of its supposed host. \textbf{INSERT NUMBER} subhalos were removed because their positions were outside of the host virial radius. \edits{Actually, are these last two okay because I'm taking the timestep right before entry instead of right after?} \textbf{INSERT NUMBER} subhalos were removed because their time of merging was earlier than their time of entry?? \edits{Need to double check that those cases weren't errors in the writing out of the file or something, I think there were only like 5 so it's weird.} Altogether, we culled about 2\% of the total sample.

@@

	%Although we have attempted to correct for these errors, there remains the possibility that erroneous cases still exist within our sample. We have made a hard cut to remove halos that gain mass, but there may be still be cases where an identification of a halo was changed within our sample. Additionally, some orbits are known to look strange or have instantaneous mass loss or gain that can be harder to properly check for. \textit{Some discussion of the cases that could possibly still exist in the data due to difficulty in being able to filter them out/ find a general way to search for them? Lots of things that double/half mass in a step and then look semi-regular again. Should I mention that? Something that gives some estimation of how many cases might be like this? To ensure that it's not some large part of the sample and the reason we can't predict things. Mention that we removed about 2\% of the total number so even if you assume the same portion is wrong it shouldn't be the source of the stochasticity?}

@@

\begin{figure*}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\textwidth]{Figures/combined_distributions_logbin}
	\vspace{-20pt}
    \caption{Distributions of the merging interactions within our sample, in two different two-dimensional spaces. The left panel shows the distribution of interactions in the space of the host mass (x-axis) and the mass ratio (y-axis) of the interaction. The right panel shows the distribution of mergers in the space of the scale of initial entry of the subhalo (x-axis) and again, the mass ratio of the interaction on the y-axis. Within each hexagonal bin, the counts of interactions are shown, on a logarithm scale, by the colorbar. Histograms show the one-dimensional distribution of host masses (above the left panel), scale of entry (above the right panel) and mass ratios to the right of the right panel). Most interactions occur at lower mass ratios and for smaller host halos, but the spaces are still well-spanned over a range of interactions in both panels. The chosen cut of 1000 particles (M = 3.215 $\times$ 10\textsuperscript{10}h\textsuperscript{-1} M\textsubscript{\(\odot\)}) for subhalos upon entry is clearly shown in the left panel. Imposing this cut and requiring that host halos be larger than their subhalos means that, for very small host halos, the only subhalos within our dataset are those with masses more similar to their hosts. Additionally, it imposes that none of our host halos have masses below 3.215 $\times$ 10\textsuperscript{10}h\textsuperscript{-1} M\textsubscript{\(\odot\)} as well.}
    \label{fig:combined_distributions_logBin}
\end{figure*}

    Our resulting sample includes a total of \textbf{INSERT NUMBER} subhalo-halo interactions, with \textbf{INSERT NUMBER} of such being mergers and \textbf{INSERT NUMBER} being survivors. Distributions of this sample with respect to host masses, mass ratios, and the scale factor of the time of entry are shown in Fig.~\ref{fig:combined_distributions_logBin}. The most common interactions in our sample are mergers of unequal masses that occurred more recently. However, our sample also spans the space of more equal mass and higher redshift mergers, with hundreds of interactions shown in many of the bins in Fig.~\ref{fig:combined_distributions_logBin}. The effects of our chosen particle cut can also be clearly seen in Fig.~\ref{fig:combined_distributions_logBin}. Because subhalos must have 1000 particles at their time of entry, this results in a minimum initial mass of 3.215 $\times$ 10\textsuperscript{10}h\textsuperscript{-1} M\textsubscript{\(\odot\)} for both the subhalo and host halo, given that a host halo must also be at least as large as its subhalo. In the left panel of Fig.~\ref{fig:combined_distributions_logBin}, this results in an area of no data with low mass hosts and unequal masses, because most subhalos of low mass hosts are too low mass to be included in our sample. \edits{Say something about if these counts are typical/ what we expect to see/ agreement with other simulations?}
\par
    For both the host halo and subhalo at the timestep of infall, and at either the timestep right before merging or at z=0, we take several physically-motivated parameters to describe the interaction between the halos. A few additional parameters were not given explicitly from Consistent-Trees merger trees, but were calculated from some set of given parameters. We divide our final set of initial parameters, which were used as input parameters to the machine learning models to make predictions, into four main categories. Internal halo parameters are those that are properties of the individual halos themselves. These parameters do not depend on the other halo in the interaction, instead giving important information about the structure of the halos as individuals. Relative halo parameters describe properties of the halos that are dependent on either other halos within the simulation or the simulation itself. Orbital parameters provide information about the initial trajectory of the subhalo's infall path. Environmental parameters describe the influence of larger scale environment around the subhalo and its host. In total, this gives us 26 input parameters, with definitions:

\vskip 0.1in
    \noindent\textbf{Internal Halo Parameters:}
    \begin{itemize}[leftmargin=.4cm,topsep=0pt]
        \item \textbf{M\textsubscript{sub}}: M\textsubscript{200b} of the subhalo. This is defined using a spherical overdensity, including only those particles that were assigned to the subhalo. Because M\textsubscript{200b} is defined using the background mass density of the universe, this definition is not affected by pseudo-evolution.
        \item \textbf{M\textsubscript{host}}: M\textsubscript{200b} of the host halo. This is defined using a spherical overdensity, including all particles that are assigned as being part of the host halo. Therefore, this mass definition also includes the mass of all subhalos within the host.
        \item \textbf{R\textsubscript{sub}}: R\textsubscript{200b} of the subhalo.
        \item \textbf{R\textsubscript{host}}: R\textsubscript{200b} of the host halo.
        \item \textbf{c\textsubscript{sub}}: the concentration of the subhalo, defined as R\textsubscript{200b}/R\textsubscript{s}, where R\textsubscript{s} is the scale radius of the subhalo.
        \item \textbf{c\textsubscript{host}}: the concentration of the subhalo, defined as R\textsubscript{200b}/R\textsubscript{s}, where R\textsubscript{s} is the scale radius of the host halo.
        \item \textbf{\textlambda\textsubscript{sub}}: Bullock spin parameter of the subhalo, defined as in \citet{Bullock2001}.
        \item \textbf{\textlambda\textsubscript{host}}: Bullock spin parameter of the host halo, defined as in \citet{Bullock2001}.
        \item \textbf{T\textsubscript{sub}}: the triaxiality parameter of the subhalo. Calculated from the definition given in \citet{Franx1991}:
        \begin{equation}
            T = \frac{1 - (b/a)^2}{1 - (c/a)^2}
        \end{equation}
        where b/a is the minor/major axis ratio and c/a is the intermediate/major axis ratio.
        \item \textbf{T\textsubscript{host}}:  the triaxiality parameter of the host halo, calculated as above.
    \end{itemize}
\vskip 0.1in
    \noindent\textbf{Relative Halo Parameters:}
    \begin{itemize} [leftmargin=.4cm,topsep=0pt]
        \item \textbf{a}: the scale factor of the universe.
        \item \textbf{M\textsubscript{ratio}}: the ratio of subhalo to host halo masses.
         \item \textbf{max(M\textsubscript{subs,sub})}: M\textsubscript{200b} of the most massive sub-subhalo within the subhalo. 0 if subhalo has no sub-substrucutre. 
